Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-07-05 edubots_surveys.Rnw
Added another paragraph to the conclusion
Added a paragraph to the conclusion section

The technology behind chatbots \cite{Gong2008,bradesko2012} has become an usual element in our everyday life, having played an important role in the development of many fields, including education and online tutoring \cite{clarizia2018,Smutny2020}, which is what we are mainly concerned with. These automatic systems ease personalized learning, 
adapting individuals' pace of learning, who get customized online tutoring outside the classroom. Thus, chatbots can significantly contribute to providing interactive learning experience as well as individual attention \cite{agarwal2020}.
Given the potential benefits that chatbots could bring to the classroom, the focus of the EDUBOTS KA2 European project [1], the sponsor of this study, is to gather, analyse and disseminate best practice of the use of chatbots in higher education institutions.  This study involves two phases of data collection. The first phase aimed to collect feedback from students about their actual needs \cite{MoraChatbots2021}.  Hence, the objective was to collect information about students’ preferences of tools/applications for chatting and messaging, how they use them in educational context, who do they like to be with in the class messaging groups, and their expectations of the chatbots in terms of assisting them during their learning process. Therefore, two surveys for bachelor and master degree students at the University of Granada (Spain) were developed and answers from more than 250 students were collected.   The key findings of the students surveys reveal that they prefer to use messaging applications, such as Telegram or WhatsApp as they are familiar to them. Students also expressed interest in chatbots that can assist them with organizing their course schedules, help them access their assignment grades and facilitate searching for course’s resources. 
The results of the first phase were fed into the second phase of the study, which focussed on teachers’ opinions about using chatbots and messaging applications in classes.  Another survey was developed for this purpose. Responses from 300 teachers were collected and analysed.  This study focuses on discussing the implications and the impact of the development of future technology-enhanced tools and educational institutions’ policies by finding answers to the following research questions: 
• RQ1 - Are teachers already using messaging apps in their classes? 
• RQ2 - Which kind of chatbots would teachers find useful in their classes? 
• RQ3 - Which kind of interaction do teachers prefer with their students? 
The remainder of the paper is organized as follows: Next is an overview of what current research has found about the use of messaging applications, including chatbots, in the classroom. The methodology used in the survey is presented in Section 3, and the results of the survey are presented next in Section 4. Finally, we discuss these results and conclude with a series of recommendations in the section that closes the paper.

>>>>

The technology behind chatbots \cite{Gong2008,bradesko2012} has become an usual element in our everyday life, having played an important role in the development of many fields, including education and online tutoring \cite{clarizia2018,Smutny2020}, which is what we are mainly concerned with. These automatic systems ease personalized learning, 
adapting individuals' pace of learning, who get customized online tutoring outside the classroom. Thus, chatbots can significantly contribute to providing interactive learning experience as well as individual attention \cite{agarwal2020}.
